---
title: "Assessment 1.1"
author: "Susie Tan s4661136"
date: "15/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

2. Create the heading of the first level and call it RMarkdown editing

# RMarkdown editing

3. Write 2-3 sentences about RMarkdown (you can google this information or use resources recommended in class - no need to reference).

R Markdown is a [.Rmd] file with records of one's research. It uses multiple languages including R, Python and SQL.

R Markdown documents are fully reproducible.  The code and command in a R Markdown file enables the researcher to reproduce his work and export the results at the click of a button.   

R Markdown uses dynamic documents that allows  researchers to export finished reports in a productive notebook interface where narrative text are weaved together to produce elegantly formatted output (eg. analysis,narration, reports, presentations and dashboards) in pdf, MS Word, or RTF documents; html, slides, Notebooks for readers and end users.

4. In the above use bold and italics for editing.

**R Markdown** is a ***[.Rmd] file*** with records of one's research. *It uses multiple languages including R, Python and SQL.*

**R Markdown** documents are ***fully reproducible.***  The ***code and command*** in a R Markdown file enables the researcher to *reproduce his work and export the results at the click of a button.*   

**R Markdown** uses ***dynamic documents*** that *allows  researchers to export finished reports in a productive notebook interface* where narrative text are weaved together to produce elegantly formatted output (eg. analysis,narration, reports, presentations and dashboards) in pdf, MS Word, or RTF documents; html, slides, Notebooks for readers and end users.

5. Review the suggested documentation on how to insert links in the .rmd file and include an in-text link to https://rmarkdown.rstudio.com/lesson-8.html

[Link to Rmarkdown Rstudio](https://rmarkdown.rstudio.com/lesson-8.html)

6. Insert an R chunk and create a variable with this dataset
https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv

The name of the variable should be `fastfood`

```{r}
library(tidyverse)

fastfood<-read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv')


#7. Display the first 10 rows of the dataset. Use Help to see how you can do this with `head()` function.

fastfood%>%head(10)


#8. Display the observations that has more than 1000 calories

fastfood%>%filter(calories>1000)


#9. Save observations with more than 40 in total_fat and more than 80 in total_carb in a new variable called `dont_eat_this`

dont_eat_this<-fastfood%>%filter(total_fat> 40 & total_carb> 80)


#10. Using the initial dataset variable, display observations from restaurant Mcdonalds
fastfood%>%filter(restaurant=='Mcdonalds')  

```